The Astropy Project

### 2017-10-20 main.tex
small fix and answer some inline comments

\section{Introduction} \label{sec:intro}
% first draft by Moritz (hamogu)
All astronomical research makes use of software in some way and
astronomy as a field has long supported the development of specialized
software tools for different astronomical tasks. Some of those
software packages are (or at least were) supported by large
institutions, e.g.~IRAF \citep[developed at NOAO,][]{IRAF}, MIDAS
\citep[developed at ESO,][]{MIDAS}, or ds9 \citep[developed at
% * <bsipocz@gmail.com> 2017-09-28T21:05:00.569Z:
%
% > or ds9
% probably starlink is a better example as being a large package of software similarly to IRAF and MIDAS rather than a single tool.
%
% ^.
% hamogu: Feel free ot swap in Starlink, if you think that's more appropriate. I picked ds9 becase (a) it's wider known (e.g. in the X-ray sounity) and (b) because it is an example of a widely used tool with institutional support that is NOT a large package. TOPCAT would have been another example if we want to expand that list.
  SAO,][]{ds9}. These packages tend to address a wide range of users
and they typically provide some level of documentation and user
support. Other packages are developed foremost by individual research
groups and used mostly in work by members of this group. Those
packages can address more specialized needs, but are not necessarily
available to the community and even if they are, documentation can in
some cases be insufficient for new users and the quality of the
software, i.e. the robustness and the level of testing that has been
performed to ensure correctness, is not always clear. On the other
hand, there are also many widely used, well documented, high quality
software packages which are developed by individuals or small groups.

@@

\subsection{Concept of affiliated packages}
% it may be described in previous subsection, if not the Brigitta can try to
% write it up
%
\par A major part of the \astropy project is the concept of ``Affiliated
Packages''. An affiliated package is an astronomy-related \python package that
is not part of the \astropypkg core package, but has requested to be
included as part of the astropy project’s community. These packages support
the goals and vision of \astropy of improving code reuse,
interoperability, and embracing good coding practices such as testing and
thorough documentation. \astropypkg currently supports both versions of
\python~2.7 and \python~3.4+, affiliated packages are strongly encouraged to
support at least \python~3.x.
%
\par Affiliated packages contain functionality that is more specialized, or
have license incompatibility, or have enough external dependencies (e.g. GUI
libraries) that limit their integration possibility into the core and thus
they are more suitable to be separate packages. In general we hope that
becoming an affiliated package is seen as a good way for new and existing
packages to gain exposure.
%
% TODO: write about the process of becoming affiliated, and project packages
%
\subsection{Mixin}

@@

\subsection{Release cycle and Long Term Support}
% This could also include information about the development cycle
% Brigitta can writes this up if there's no other taker
\inlinecomment{BMS: TODO}{reference APE2 for versioning and APE10 for dropping python2 support}
\inlinecomment{BMS}{shall we maybe refer to the release calendar, too?}
\inlinecomment{BMS}{should we mention that v3.0 is the exception to the
  version numbering scheme we use by not being 2.1?}
%
\par The general scheme for the releases and version numbering that the core
package has adopted if the following. \astropypkg has new feature releases every
6 months, and between feature releases additional bugfix releases that
contain only bugfixes but no new features.
% The timing of
%
\par Long-term support (LTS) releases continue to receive bugfixes for 2
years with no changes to the API. They are ideal for pipelines and other
applications where API stability is essential. The latest LTS release is
also the last one that supports \python 2, and will receive bug fixes until the
end of 2019.
%
\par The version numbering of \astropypkg reflects on the release scheme
described above. The core package uses the form x.y.z, where x is advances
on LTS, y is advanced for a non-LTS feature release, and z is advanced on
bugfix releases.

>>>>

\section{Introduction} \label{sec:intro}
% first draft by Moritz (hamogu)
All astronomical research makes use of software in some way and
astronomy as a field has long supported the development of specialized
software tools for different astronomical tasks. Some of those
software packages are (or at least were) supported by large
institutions, e.g.\ IRAF \citep[developed at NOAO,][]{IRAF}, MIDAS
\citep[developed at ESO,][]{MIDAS}, or ds9 \citep[developed at
% * <bsipocz@gmail.com> 2017-09-28T21:05:00.569Z:
%
% > or ds9
% probably starlink is a better example as being a large package of software similarly to IRAF and MIDAS rather than a single tool.
%
% ^.
% hamogu: Feel free ot swap in Starlink, if you think that's more appropriate. I picked ds9 becase (a) it's wider known (e.g. in the X-ray sounity) and (b) because it is an example of a widely used tool with institutional support that is NOT a large package. TOPCAT would have been another example if we want to expand that list.
  SAO,][]{ds9}. These packages tend to address a wide range of users
and they typically provide some level of documentation and user
support. Other packages are developed foremost by individual research
groups and used mostly in work by members of this group. Those
packages can address more specialized needs, but are not necessarily
available to the community and even if they are, documentation can in
some cases be insufficient for new users and the quality of the
software, i.e. the robustness and the level of testing that has been
performed to ensure correctness, is not always clear. On the other
hand, there are also many widely used, well documented, high quality
software packages which are developed by individuals or small groups.

@@

\subsection{Concept of affiliated packages}
% it may be described in previous subsection, if not the Brigitta can try to
% write it up
%
\par A major part of the \astropy project is the concept of
``Affiliated Packages''. An affiliated package is an astronomy-related
\python package that is not part of the \astropypkg core package, but
has requested to be included as part of the astropy project’s
community. These packages support the goals and vision of \astropy of
improving code reuse, interoperability, and embracing good coding
practices such as testing and thorough documentation. \astropypkg
version 2.0 supports \python~2.7 and \python~3.4+, affiliated packages
are strongly encouraged to support at least \python~3.x.
%
\par Affiliated packages contain functionality that is more specialized, or
have license incompatibility, or have enough external dependencies (e.g. GUI
libraries) that limit their integration possibility into the core and thus
they are more suitable to be separate packages. In general we hope that
becoming an affiliated package is seen as a good way for new and existing
packages to gain exposure.
%
% TODO: write about the process of becoming affiliated, and project packages
%
\subsection{Mixin}

@@

\subsection{Release cycle and Long Term Support}
% This could also include information about the development cycle
% Brigitta can writes this up if there's no other taker
\inlinecomment{BMS: TODO}{reference APE2 for versioning and APE10 for dropping python2 support}
\inlinecomment{BMS}{shall we maybe refer to the release calendar, too?}
\inlinecomment{hamogu}{I don't think that's necessary. These details are in the docs, but not too important for a general paper.}
\inlinecomment{BMS}{should we mention that v3.0 is the exception to the
  version numbering scheme we use by not being 2.1?}
\inlinecomment{hamogu}{No. This is a genral paper, those are details that will be unimportant very soon. }
%
\par The general scheme for the releases and version numbering that the core
package has adopted if the following. \astropypkg has new feature releases every
6 months, and between feature releases additional bugfix releases that
contain only bugfixes but no new features.
% The timing of
%
\par Long-term support (LTS) releases continue to receive bugfixes for 2
years with no changes to the API. They are ideal for pipelines and other
applications where API stability is essential. The latest LTS release is
also the last one that supports \python 2, and will receive bug fixes until the
end of 2019.
%
\par The version numbering of \astropypkg reflects on the release scheme
described above. The core package uses the form x.y.z, where x is advances
on LTS, y is advanced for a non-LTS feature release, and z is advanced on
bugfix releases.
